\hypertarget{index_intro_sec}{}\section{Introduction}\label{index_intro_sec}
This is the documentation for Vgm Player Library for the Arduino platform. The Vgm Player Library provides a simple library to read Video Game Music (V\+GM) files from an SD card and play them on real hardware audio chips.\hypertarget{index_dependencies}{}\section{Dependencies}\label{index_dependencies}
This library depends on \href{https://github.com/greiman/SdFat}{\tt Sd\+Fat} being present on your system. Please make sure you have installed the latest version before using this library.\hypertarget{index_author}{}\section{Author}\label{index_author}
Written by Andrés Mata for Pens\+Actius.\hypertarget{index_license}{}\section{License}\label{index_license}
Copyright (C) 2018 Andrés Mata Bretón

This program is free software; you can redistribute it and/or modify it under the terms of the G\+NU General Public License as published by the Free Software Foundation; either version 3 of the License, or (at your option) any later version.

This program is distributed in the hope that it will be useful, but W\+I\+T\+H\+O\+UT A\+NY W\+A\+R\+R\+A\+N\+TY; without even the implied warranty of M\+E\+R\+C\+H\+A\+N\+T\+A\+B\+I\+L\+I\+TY or F\+I\+T\+N\+E\+SS F\+OR A P\+A\+R\+T\+I\+C\+U\+L\+AR P\+U\+R\+P\+O\+SE. See the G\+NU General Public License for more details.

You should have received a copy of the G\+NU General Public License along with this program; if not, write to the Free Software Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA 02110-\/1301 U\+SA 